---
title: "STA523 HW6"
author: "Shaoji Li, Faustine Li, Eden Huang, Yumemichi Fujita"
date: "11/14/2016"
output: html_document
---

## Setup

```{r}
library(raster, quietly = T) # load before dplyr to avoid select bs

library(dplyr, quietly = T)
library(ggplot2, quietly = T)
library(sf, quietly = T)
library(sp, quietly = T)
library(randomForest, quietly = T)
```

## Task 1 GeoCoding

```{r}
# load data
load('/data/nyc_parking/NYParkingViolations.Rdata')
pluto = st_read('/data/nyc_parking/pluto_manhattan/MNMapPLUTO.shp')

# filter pluto to address, longitude and latitude
pluto_xy = data.frame(
    pluto$Address,
    st_centroid(pluto) %>%
        unlist() %>%
        matrix(ncol=2,byrow=TRUE),
    stringsAsFactors = FALSE
) %>%
    setNames(c('address', 'x', 'y'))

# filter nyc to address and precint
man_precincts = c(1, 5, 6, 7, 9, 10, 13, 14, 17, 18, 19, 20, 22, 23,
                    24, 25, 26, 28, 30, 32, 33, 34)
nyc_man = nyc %>%
    mutate(address = paste(House.Number, Street.Name)) %>%
    filter(Violation.Precinct %in% man_precincts) %>%
    select(address, precinct = Violation.Precinct)

rm(nyc, pluto)

# Clean data -------------------------------------------------------------

# make sure data is in the right case
nyc_man$address  = sapply(nyc_man$address, toupper)
pluto_xy$address = sapply(pluto_xy$address, toupper)

# remove NA values due to no house address
nyc_man$address = gsub('\\bNA \\b', '', nyc_man$address)

# remove special characters, double spaces, etc...
special_char = c('\\.', '\\,', '\\!', '\\#', '\\?', '(?<= ) +')

for (i in seq_along(special_char)) {
    pluto_xy$address = gsub(special_char[i], '',
                            pluto_xy$address, perl = TRUE)
    nyc_man$address  = gsub(special_char[i], '',
                            nyc_man$address, perl = TRUE)
}

# replace place and street abbreviations with long form
# E with EAST, PL with PLACE, ST with STREET, etc...
abbrev = rbind( c('(?<!\\/)\\bE\\b(?!\\/)', 'EAST'),
                c('(?<!\\/)\\bW\\b(?!\\/)', 'WEST'),
                c('(?<!\\/)\\bS\\b(?!\\/)', 'SOUTH'),
                c('(?<!\\/)\\bN\\b(?!\\/)', 'NORTH'),
                c('\\bPL\\b', 'PLACE'),
                c('\\bAV[E]?\\b', 'AVENUE'),
                c('\\bBLV[D]?\\b', 'BOULEVARD'),
                c('\\bCT\\b', 'COURT'),
                c('\\bCIR\\b', 'CIRCLE'),
                c('\\bDR[V]?\\b', 'DRIVE'),
                c('\\bLN\\b', 'LANE'),
                c('\\bRD\\b', 'ROAD'),
                c('\\bST$', 'STREET'),
                c('\\bSTR[T]?\\b', 'STREET'),
                c('\\bPLZ\\b', 'PLAZA'),
                c('\\bMT\\b', 'MOUNT')
                )

for (i in seq_len(nrow(abbrev))) {
    pluto_xy$address = gsub(abbrev[i,1], abbrev[i,2],
                            pluto_xy$address, perl = TRUE)
    nyc_man$address  = gsub(abbrev[i,1],abbrev[i,2],
                            nyc_man$address, perl = TRUE)
}

# remove ordinal names, 1ST to 1, 2ND to 2, 3RD to 3, etc...
ord = c('(?<=[0-9])ST\\b', '(?<=[0-9])ND\\b', '(?<=[0-9])RD\\b',
        '(?<=[0-9])TH\\b')

for (i in seq_along(ord)) {
    pluto_xy$address = gsub(ord[i], '',
                            pluto_xy$address, perl = TRUE)
    nyc_man$address  = gsub(ord[i], '',
                            nyc_man$address, perl = TRUE)
}

# new york street specific fixes
man_names = rbind(c('\\bBWAY\\b', 'BROADWAY'),
                  c('\\bST RI NY 10044\\b', 'STREET'),
                  c('\\bF D R\\b', 'FDR')
)

for (i in seq_len(nrow(man_names))) {
    pluto_xy$address = gsub(man_names[i,1], man_names[i,2],
                            pluto_xy$address, perl = TRUE)
    nyc_man$address  = gsub(man_names[i,1], man_names[i,2],
                            nyc_man$address, perl = TRUE)
}

# merging data ----------------------------------------------------------

nyc_geo = inner_join(nyc_man, pluto_xy)
save(nyc_geo, file = 'nyc_geo.Rdata')
```



## Task 2: Recreating NYC’s Police Precincts

Load data and plot the precincts on map to get an idea of the boundaries
```{r}
load(file="nyc_geo.Rdata")
# ggplot(nyc_geo, aes(x=x,y=y,color=factor(precinct))) + geom_point()
latlon=data.frame("lon" = nyc_geo$x, "lat" = nyc_geo$y)
coord=SpatialPoints(latlon)
plot(coord, col=nyc_geo$precinct, pch=18, cex=0.5, axes=TRUE)
```

Get Manhattan Info

```{r}
nybb = st_read("/data/nyc_parking/nybb/", quiet=TRUE)
manh = nybb %>% filter(BoroName == "Manhattan")
#plot(manh,axes=TRUE)

library(raster)
ext = st_bbox(manh) %>% .[c("xmin","xmax","ymin","ymax")] %>% extent()
r = raster(ext, ncol=100, nrow=300)
r = rasterize(as(manh,"Spatial"),r)
plot(r)
```

Get prediction locations

```{r}
pred_cells = which(!is.na(r[]))
pred_locs = xyFromCell(r, pred_cells) %>% as_data_frame()
plot(pred_locs, pch=16, cex=0.1)
```

Identify outliers of each precinct, so get rid of the 1% extreme values of each precinct (except for 22 since it only has 252 points) and sample 3% of the values. Instead, I duplicate the size of precinct 22 by 10

```{r}
nyc_geo_reduced = NULL
for (p in man_precincts) {
  if (p == 22) {
    res = nyc_geo[which(nyc_geo$precinct == p),]
    nyc_geo_reduced = rbind(nyc_geo_reduced,
                            do.call("rbind", replicate(10, res, simplify = FALSE)))
  } else {
    res = nyc_geo[which(nyc_geo$precinct == p),]
    lon.quantile = unname(quantile(res$x, probs = c(0.005, 0.995)))
    lat.quantile = unname(quantile(res$y, probs = c(0.005, 0.995)))
    res.filt = res[(res$x <= lon.quantile[2] & res$x >= lon.quantile[1]) &
                     (res$y <= lat.quantile[2] & res$y >= lat.quantile[1]),]
    n = nrow(res.filt)
    idx = sort(sample(1:n,round(0.03*n),replace = F))
    res.filt.samp = res.filt[idx,]
    nyc_geo_reduced = rbind(nyc_geo_reduced, res.filt.samp)
  }
}
```

Perform Random Forest and predict

```{r}
model = randomForest(as.factor(precinct)~x+y,data=nyc_geo_reduced,na.action = na.omit,cross=5)
rf.pred = predict(model,pred_locs)
r.rf = r
r.rf[pred_cells] = as.numeric(rf.pred)
```

Draw the polygons

```{r}
source("polygonizer.R")
p = polygonizer(r.rf)
p = st_transform(p, 4326)
plot(p)
```

